Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-03-23 analysis/paper/shceof.Rmd
Justifica mejor la rotación de los cEOFs

The phase of cEOFs is defined up to an additive constant.
For real EOFs, this constant can be either 0 or $\pi$, corresponding to a change in sign.
For cEOFs, it can be any real number between 0 and $2\pi$ [@horel1984], corresponding to rotations in the complex plane.
Since any choice is arbitrary and equally valid, we chose the phase of each cEOF so that the real and imaginary parts are aligned with meaningful phases in our analysis.
This procedure does not create a spurious correlation, it only takes an existing relationship and aligns it with a specific phase.
For the first complex principal component, the phase was chosen so that the time series corresponding to the real part has the maximum correlation with the zonal wave 1 of Total Ozone Column between `r knitr::combine_words(LatLabel(o3wave_lats))`.
This also nearly minimises the correlation with the imaginary part.
For the second complex principal component, the phase was chosen so that the coefficient of determination between the Oceanic Niño Index [@bamston1997] and the real part was minimized, which also nearly maximizes the correlation with the imaginary part.

>>>>

The phase of cEOFs is defined up to an additive constant.
For real EOFs, this constant can be either 0 or $\pi$, corresponding to a change in sign.
For cEOFs, it can be any real number between 0 and $2\pi$ [@horel1984], corresponding to rotations in the complex plane.
Since any choice is arbitrary and equally valid, we chose the phase of each cEOF so that the real or imaginary parts are aligned with meaningful phases in our analysis.

Preliminary analysis showed that the first cEOF was closely related to the the zonal wave 1 of Total Ozone Column and the second cEOF was closely related to ENSO. 
Therefore, to aid in the interpretation, we chose the phases of each cEOF so that these relationships are aligned with one of the complex components.

We chose the phase of cEOF1 so that the time series corresponding to the real part has the maximum correlation with the zonal wave 1 of Total Ozone Column between `r knitr::combine_words(LatLabel(o3wave_lats))`. 
And we chose the phase of cEOF2 so that the coefficient of determination between the Oceanic Niño Index [@bamston1997] and the real part is minimized, which also nearly maximizes the correlation with the imaginary part.

This procedure does not create spurious correlations, it only takes an existing relationship and aligns it with a specific phase.
